---
title: "Functions relating to the Colonization model"
output: 
  html_notebook: 
    highlight: tango
    theme: cerulean
    toc: yes
---
#Load packages

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
```
# Model 

According to the data simulation function:

A = p1 p2 a
B = p1 (1-p2 a)
C = (1-p1) p2
D = (1-p1) (1-p2)

Alpha reduces the colonization of pathogen ONLY when mycorrhiza is present. The interaction also ONLY has an effect on the pathogen colonization, not the mycorrhizal colonization. 

The nice thing about this model is that it inhibits the pathogen at every point that there is a mycorrhiza. 

The problem with this model is that the proportion of area colonized with mycorrhiza does not have an effect on how the pathogens will colonize the non-mycorrhizal points. If the effect is systemic, this will be something we see. 
  
  
# Data Simulation 

```{r Data simulation}
GMsim<-function(NXsec=100,NPlants=1000,Pm=0.5,Pp=0.2,Pc=0.5){
  c<-0
  Root<-data.frame(ind=rep(NA,NPlants*NXsec),c1=rep(NA,NPlants*NXsec),c2=rep(NA,NPlants*NXsec)) # Data for saving output
  for(i in 1:NPlants){
    tempMyc<-sample(1:0,NXsec,replace=T,prob=c(Pm,1-Pm)) # Generate Myc colonization
    tempPath<-rep(NA,NXsec) # Empty vector of pathogen infection
    
    # Simulate root cross-sections. 
    if(length(tempMyc[tempMyc==0])>0){
      tempPath[tempMyc==0]<-sample(1:0,length(tempPath[tempMyc==0]),replace=T,prob=c(Pp,1-Pp))  
    }
    if(length(tempPath[tempMyc==1])>0){
      tempPath[tempMyc==1]<-sample(1:0,length(tempPath[tempMyc==1]),replace=T,prob=c(Pp*Pc,1-Pp*Pc))
    }
    
    # Add the simulated co-occurence to the simulated data
    Root[(c+1):(c+NXsec),1]<-rep(i,NXsec)
    Root[(c+1):(c+NXsec),2]<-tempMyc
    Root[(c+1):(c+NXsec),3]<-tempPath
    
    #counter
    c<-c+NXsec
    
    # Clear temporary vectors to avoid errors in future iterations
    tempMyc<-tempPath<-NA
  }
  return(Root) ## Don't forget to return this to the user!
}


Toy<-GMsim()
```


# Function for Var/covar and correlation 

data -- the dataset with rows representing each cross-section and the following columns:

ind -- the column with the labels for individuals; there should be > 1 location per individual

c1 -- the column of presence/absence (1:0) for Mycorrhiza

c2 -- the column of presence/absence (1:0) for Pathogen



```{r Var/covar and  corr coeff Function }
Bcor<-function(x=NA,ind=ind,c1=c1,c2=c2){
  # Check if user wants covariance matrix or correlation coefficient
  
  # Calculate the frequency of each possible outcome
A<- length((dplyr::filter(x, c1 == 1 & c2 == 1))$ind)
B<- length((dplyr::filter(x, c1 == 1 & c2 == 0))$ind)
C<- length((dplyr::filter(x, c1 == 0 & c2 == 1))$ind)
D<- length((dplyr::filter(x, c1 == 0 & c2 == 0))$ind)
  
  # Calculate variances, covariance and correlation
infoDF <- data.frame(VARIANCE1=NA,VARIANCE2=NA,COVARIANCE=NA,CORRELATION=NA)
infoDF$VARIANCE1[1] <- (A+B)*(1-(A+B))
infoDF$VARIANCE2[1] <- (A+C)*(1-(A+C))
infoDF$COVARIANCE[1]<- A-(A+B)*(A+C)
infoDF$CORRELATION[1] <- infoDF$COVARIANCE[1]/(sqrt(infoDF$VARIANCE1[1]*infoDF$VARIANCE2[1]))

    return(print(infoDF))
}
```



## Test

```{r}
Toy<-GMsim(Pm=0.6,Pp=0.2,Pc=0.3)
Bcor(x = Toy)

```


# Function for p1, p2 and a

```{r p1 p2 a Function }


Icor <- function(x=NA,ind=ind,c1=c1,c2=c2){
  # Conditional probabilities
  ## A through B can be estimated from the data
  ## Use these equations to try to solve for p1, p2 & a
  ## For example, B-C or C-B will isolate p1 and p2 only
A<- length((dplyr::filter(x, c1 == 1 & c2 == 1))$ind)
B<- length((dplyr::filter(x, c1 == 1 & c2 == 0))$ind)
C<- length((dplyr::filter(x, c1 == 0 & c2 == 1))$ind)
D<- length((dplyr::filter(x, c1 == 0 & c2 == 0))$ind)

  # Calculate p1,p2 and a
  # note that there are two versions of p1 and p2 because of the quadratic equation
  # choose the one that has a positive value. 

infoDF <- data.frame(MycP=NA,PathP=NA, alpha=NA)

  infoDF$MycP[1]<- 1-((C+D)/sum(A,B,C,D))
  infoDF$PathP[1]<- (C/sum(A,B,C,D))/(1-p1)
  infoDF$alpha[1]<- (A/sum(A,B,C,D))/(p1*p2) 

  return(print(infoDF))
}



```

## Test

```{r}
Toy<-GMsim(Pm=0.6,Pp=0.2,Pc=0.3)
Icor(x = Toy)
```




#Our data
##Load data
```{r Introduce co-occurence dataset, message=FALSE, warning=FALSE, echo=FALSE}
mdata <- read.csv("./Assessing_Oct_20.csv",stringsAsFactors=F)
indiv <- mdata$CODE[!mdata$CODE==""]
tdata <- mdata[grep("[0-9]+",mdata$Cross),]
nrow(tdata)/length(indiv)

# This is not the same because some individuals just had the totals not the cooccurence data
## THE COMMENT IS NOT CLEAR, EXPLAIN...
indiv2 <- tdata$CODE[!tdata$CODE==""]
nrow(tdata)/length(indiv2)
indiv2 <- data.frame(indiv2)
indiv2 <- mefa:::rep.data.frame(indiv2,each=100)
fdata <- cbind(indiv2,tdata)
fdata <- fdata[,-c(2,3,4,9,14,17,18)]

# Cleaning up the occurence data
## CLEANING UP HOW?
fdata[is.na(fdata)] <- 0
fdata$Lesion<-rowSums(fdata[,2:4])
fdata[fdata$Lesion>1,]
fdata$Mycorrhiza<-rowSums(fdata[,6:8])
fdata[fdata$Mycorrhiza>1,]
fdata <- fdata[,-c(2:4,6:8)]

#### Checking data for problems ####

summary(fdata)
fdata$None.Path <- as.integer(fdata$None.Path)
fdata$None.Myc <- as.integer(fdata$None.Myc)
fdata[is.na(fdata)] <- 0 


sherb <- fdata$Herbivory+fdata$None.Herb
fdata[sherb!=1,]
fdata[sherb!=1,"None.Herb"]<-1

# Are all the sums equal to 100 for herb? 
dframeHerb <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeHerb[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeHerb$counter[c] <- c
  dframeHerb$Indiv2[c] <- i
  dframeHerb$Sum[c] <- sum(subdata[,"Herbivory"]+subdata[,"None.Herb"])
  subdata <- NA
  c <- c + 1
}
dframeHerb[dframeHerb$Sum!=100,]


# Are all the sums equal to 100 for Mycorrhiza? 
dframeMyc <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeMyc[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeMyc$counter[c] <- c
  dframeMyc$Indiv2[c] <- i
  dframeMyc$Sum[c] <- sum(subdata[,"Mycorrhiza"]+subdata[,"None.Myc"])
  subdata <- NA
  c <- c + 1
}
dframeMyc[dframeMyc$Sum!=100,]


# Are all the sums equal to 100 for Lesions? 
dframeLesion <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeLesion[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeLesion$counter[c] <- c
  dframeLesion$Indiv2[c] <- i
  dframeLesion$Sum[c] <- sum(subdata[,"Lesion"]+subdata[,"None.Path"])
  subdata <- NA
  c <- c + 1
}
dframeLesion[dframeLesion$Sum!=100,]


# Separating "Individual" into: pop,location,species columns 
fdata$pop <- gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",fdata$indiv)
fdata$location <- gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",fdata$indiv)
fdata$species <- sub("^[0-9]+[I,O]([A-Z]+).*","\\1",fdata$indiv)
fdata$location <- as.factor(fdata$location)
fdata$species <- as.factor(fdata$species)
fdata$pop <- as.factor(fdata$pop)
fdata$indiv2 <- as.character(fdata$indiv2)
summary(fdata)
fdata %>% drop_na()->fdata

fdata$None.Myc <- as.factor(fdata$None.Myc)
fdata$Herbivory <- as.factor(fdata$Herbivory)
fdata$Mycorrhiza <- as.factor(fdata$Mycorrhiza)
fdata$Lesion <- as.factor(fdata$Lesion)
fdata$None.Herb <- as.factor(fdata$None.Herb)
fdata$None.Path <- as.factor(fdata$None.Path)
summary(fdata)
```

```{r Species specific}
levels(fdata$species)
dataAH <-filter(fdata,species== "AH")[,c(1,6,7,8,9)]
colnames(dataAH)<-c("ind","c1","c2","pop","location")
Bcor(dataAH)
Icor(dataAH)

dataCL <-filter(fdata,species== "CL")[,c(1,6,7,8,9)]
colnames(dataCL)<-c("ind","c1","c2","pop","location")
Bcor(dataCL)
Icor(dataCL)

dataGA <-filter(fdata,species== "GA")[,c(1,6,7,8,9)]
colnames(dataGA)<-c("ind","c1","c2","pop","location")
Bcor(dataGA)
Icor(dataGA)

dataGR <-filter(fdata,species== "GR")[,c(1,6,7,8,9)]
colnames(dataGR)<-c("ind","c1","c2","pop","location")
Bcor(dataGR)
Icor(dataGR)

dataMR <-filter(fdata,species== "MR")[,c(1,6,7,8,9)]
colnames(dataMR)<-c("ind","c1","c2","pop","location")
Bcor(dataMR)
Icor(dataMR)

dataSC <-filter(fdata,species== "SC")[,c(1,6,7,8,9)]
colnames(dataSC)<-c("ind","c1","c2","pop","location")
Bcor(dataSC)
Icor(dataSC)
```

```{r Location specific}
dataInside <-filter(fdata,location== "I")[,c(1,6,7,8,10)]
colnames(dataInside)<-c("ind","c1","c2","pop","species")
Bcor(dataInside)
Icor(dataInside)

dataOutside <-filter(fdata,location== "O")[,c(1,6,7,8,10)]
colnames(dataOutside)<-c("ind","c1","c2","pop","species")
Bcor(dataOutside)
Icor(dataOutside)
```


```{r Species and location specific}

dataAHIn <-filter(fdata,species== "AH" & location== "I")[,c(1,6,7,8)]
colnames(dataAHIn)<-c("ind","c1","c2","pop")
Bcor(dataAHIn)
Icor(dataAHIn)

dataAHOut <-filter(fdata,species== "AH" & location== "O")[,c(1,6,7,8)]
colnames(dataAHOut)<-c("ind","c1","c2","pop")
Bcor(dataAHOut)
Icor(dataAHOut)

dataCLIn <-filter(fdata,species== "CL" & location== "I")[,c(1,6,7,8)]
colnames(dataCLIn)<-c("ind","c1","c2","pop")
Bcor(dataCLIn)
Icor(dataCLIn)

dataCLOut <-filter(fdata,species== "CL" & location== "O")[,c(1,6,7,8)]
colnames(dataCLOut)<-c("ind","c1","c2","pop")
Bcor(dataCLOut)
Icor(dataCLOut)

dataGAIn <-filter(fdata,species== "GA"& location== "I")[,c(1,6,7,8)]
colnames(dataGAIn)<-c("ind","c1","c2","pop")
Bcor(dataGAIn)
Icor(dataGAIn)

dataGAOut <-filter(fdata,species== "GA"& location== "O")[,c(1,6,7,8)]
colnames(dataGAOut)<-c("ind","c1","c2","pop")
Bcor(dataGAOut)
Icor(dataGAOut)

dataGRIn <-filter(fdata,species== "GR" & location== "I")[,c(1,6,7,8)]
colnames(dataGRIn)<-c("ind","c1","c2","pop")
Bcor(dataGRIn)
Icor(dataGRIn)

dataGROut <-filter(fdata,species== "GR" & location== "O")[,c(1,6,7,8)]
colnames(dataGROu)<-c("ind","c1","c2","pop")
Bcor(dataGROu)
Icor(dataGROu)

dataMRIn <-filter(fdata,species== "MR" & location== "I")[,c(1,6,7,8)]
colnames(dataMRIn)<-c("ind","c1","c2","pop")
Bcor(dataMRIn)
Icor(dataMRIn)

dataMROut <-filter(fdata,species== "MR" & location== "O")[,c(1,6,7,8)]
colnames(dataMROut)<-c("ind","c1","c2","pop")
Bcor(dataMROut)
Icor(dataMROut)

dataSC <-filter(fdata,species== "SC")[,c(1,6,7,8)]
colnames(dataSC)<-c("ind","c1","c2","pop")
Bcor(dataSC)
Icor(dataSC)
```


